### 2015-05-20 reports/paper/introduction.tex
paper update

Accuracte indoor locazation allows creation of noval applications with surrounding awareness that uses position and movment information as input. One application is to allow users to draw with music, without physically touching the computer. Another example is to build AI games with physical pieces such as toy car racing where the computer controls some of the pieces. In this work, we aim to build such a source localization system that is portable, inexpensive, yet accuracte for localization in a small area.

@@

Bluetooth and Wi-Fi based technologies gained popularity in indoor positioning recently, mainly due to the widespread deployment of bluetooth tags and Wi-Fi stations in public spaces. In these systems, signal strength received from different base stations are used for the estimation of the device location. However, their reported accuracy are in the range of $1$ to $5$ meters~\cite{intro:blue, intro:loc}, which is not enough for local movement tracking.

@@

In this paper, we discuss prior relevant research and the theory in sound localization in Section II. In Section III, we carried out a simulation to evaluate different array achitectures and their impact on accuracy. In Section IV, we present the chosen architecture along with hardware details. Finally, we provide the experiment details and results in Section V.

>>>>

Accuracte indoor locazation allows creation of noval applications with surrounding awareness that uses position and movment information as input. One application is to allow users to draw with music, without physically touching the computer. Another example is to build AI games with physical pieces such as toy car racing where the computer controls some of the pieces. In this work, we aim to build such a source localization system that is portable, inexpensive, yet resonably accuracte for localization in a small area.

@@

Bluetooth and Wi-Fi based technologies have gained popularity in indoor positioning recently, mainly due to the widespread deployment of bluetooth tags and Wi-Fi stations in public spaces. In these systems, signal strength received from different base stations are used for the estimation of the device location. However, their reported accuracy are in the range of $1$ to $5$ meters~\cite{intro:blue, intro:loc}, which is not enough for local movement tracking.

@@

In this paper, we discuss prior relevant research and the theory in sound localization in Section II. In Section III, we evaluated different array achitectures and their impact on accuracy. We demonstrated that a two array system outperforms a single array system of similar size. In Section IV, we present the chosen architecture along with hardware details. Finally, experiment details and results are presented in Section V.
